Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Fix todo about Table 3 labels
Address comment from review 2A about connectionless send

The API that is exposed to applications using TCP is invisible from the
network, and can be changed. Relaxing the API to enable out-of-order
delivery of segments is trivial: segments are delivered to the application
in the order that they arrive, with their TCP sequence attached. The TCP
sequence number can be passed to the application using the existing
Berkeley sockets API, either with the received data, or using
\texttt{getsockopt()}. Out-of-order delivery is not useful when using a
byte-stream abstraction, and so the API should be further modified to
provide a message-oriented abstraction. The Berkeley sockets API already
supports such an abstraction for datagram protocols.

@@

\todo{Review A: Section 3 should also note that connectionless send and
receive already work on connection-oriented sockets}

>>>>

The API that is exposed to applications using TCP is invisible from the
network, and can be changed.  For example, TCP Fast Open \cite{RFC7413} 
has been implemented by overloading the connectionless \texttt{sendto()} 
call to trigger an implicit \texttt{connect()} when used on an unconnected
TCP socket.
Relaxing the API to enable out-of-order
delivery of segments is trivial: segments are delivered to the application
in the order that they arrive, with their TCP sequence attached. The TCP
sequence number can be passed to the application using the existing
Berkeley sockets API, either with the received data, or using
\texttt{getsockopt()}. Out-of-order delivery is not useful when using a
byte-stream abstraction, and so the API should be further modified to
provide a message-oriented abstraction. The Berkeley sockets API already
supports such an abstraction for datagram protocols.

@@
